Generalization Errors of Hard Parameter Sharing: High-dimensional Asymptotics and Implications

### 2020-09-25 arxiv/implications.tex
revise

We now discuss two implications of Corollary \ref{cor_MTL_loss} and Claim \ref{claim_STL_loss} regarding the information transfer in MTL: the transition from positive transfer to negative transfer with respect to varying model distance and varying sample ratio, respectively.

>>>>

We now discuss two implications of Corollary \ref{cor_MTL_loss} and Claim \ref{claim_STL_loss} regarding the information transfer in MTL: the transitions from positive transfer to negative transfer with respect to varying model distance and varying sample ratio, respectively.

### 2020-09-25 arxiv/proof_examples.tex
revise

\begin{proof}[Proof of Claim \ref{claim_covar_shift}]	
	With the same arguments as in Claim \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds. Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify $g(M_0)$ as
\be \nonumber
\begin{split}
g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \quad \text{w.h.p.}
\end{split}
\ee
 for some constant $\e>0$. In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $ \mu_{\min}\le \lambda_p(M)\le \lambda_1(M)\le \mu_{\max}$. We omit the details here. 
 \end{proof}

@@

\subsection{Covariate Shift}\label{app_proof_33}

Finally, in this subsection we prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}_2^{\MTL})$ is minimized approximately when $M$ is a scalar matrix, provided that there is enough source data.

\item[(iii)] If $n_1=n_2$, we have $f(\lambda)=f(1)=2/(1-\gamma)$, which means $\te(\hat \beta_{2}^{\MTL},\lambda)$ and $\te(\hat \beta_{2}^{\MTL},1)$ are roughly the same. %, which explains why the curves in Figure  \ref{fig_model_shift_phasetrans} (c) all cross at the point $n_1=n_2$.
\end{itemize}
This also partially justifies Proposition \ref{prop_covariate}. %Theorem  the observations in Figure \ref{fig_model_shift_phasetrans} (c), 
\end{proof}
\fi
%\todo{add a transition example}

>>>>

%\subsection{Covariate Shift}\label{app_proof_33}

Finally, we prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}_2^{\MTL})$ is minimized approximately when $M$ is a scalar matrix, provided that there is enough source data.

%\begin{proof}[Proof of Claim \ref{claim_covar_shift}]	
%	With the same arguments as in Claim \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds. Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify $g(M_0)$ as
%\be \nonumber
%\begin{split}
%g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \quad \text{w.h.p.}
%\end{split}
%\ee
% for some constant $\e>0$. In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $ \mu_{\min}\le \lambda_p(M)\le \lambda_1(M)\le \mu_{\max}$. We omit the details here. 
% \end{proof}

\item[(iii)] If $n_1=n_2$, we have $f(\lambda)=f(1)=2/(1-\gamma)$, which means $\te(\hat \beta_{2}^{\MTL},\lambda)$ and $\te(\hat \beta_{2}^{\MTL},1)$ are roughly the same. %, which explains why the curves in Figure  \ref{fig_model_shift_phasetrans} (c) all cross at the point $n_1=n_2$.
\end{itemize}
This also partially justifies Proposition \ref{prop_covariate}. %Theorem  the observations in Figure \ref{fig_model_shift_phasetrans} (c), 
\end{proof}
\fi

@@

%\todo{add a transition example}
